Associations between Chlorophyll *a* and various Microcystin-LR Health Advisory

### 2015-09-21 manuscript/manuscript.Rmd
update

```{r chla_micro_scatter, echo=FALSE, fig.width=6, fig.cap="Scatterplot showing association betweeen chlorophyll \\textit{a} and microcystin-LR. \\label{fig:chla_micro_scatter}"}
plot_scatter(nla_dat,xvar="log_chla",yvar = "log_micro",pt_col=viridis(1),
             x=expression(paste('Log10 Chl ', italic("a"),' (',mu,'g/L)')),
             y=expression(paste('Log10 microcystin-LR',' (',mu,'g/L)')))
```

>>>>

```{r chla_micro_scatter, echo=FALSE, fig.width=6, fig.cap="Scatterplot showing association betweeen chlorophyll \\textit{a} and microcystin-LR. \\label{fig:chla_micro_scatter}"}
plot_scatter(nla_dat,xvar="log_chla",yvar = "log_micro",cat="WSA_ECO9",
             x=expression(paste('Log10 Chl ', italic("a"),' (',mu,'g/L)')),
             y=expression(paste('Log10 microcystin-LR',' (',mu,'g/L)')))
```
